---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# framrosetta

<!-- badges: start -->
<!-- badges: end -->

`framrosetta` is a data library of look up tables for translating FRAM fisheries, stocks, and areas to other fishery data.


## Installation

You can install `framrosetta` like so:

```r
devtools::install_github("FRAMverse/framrosetta")    
```

or

```r
pak::pkg_install("FRAMverse/framrosetta")
```

```{r}
library(framrosetta)
```

## Table summaries

`framrosetta` contains the following tables for translating FRAM fisheries, stocks, and areas to other fishery data or human readable formats:


### `rmis_fram`

Translating between FRAM and RMIS.

```{r, results = 'asis'}
knitr::kable(head(rmis_fram, 5))
```

### `tocas_fram`

Translating between FRAM and TOCAS.

```{r, results = 'asis'}
knitr::kable(head(tocas_fram, 5))
```

### `waft_fram`

Translating between WAFT and FRAM.

```{r, results = 'asis'}
knitr::kable(head(waft_fram, 5))
```


### `stock_chinook_fram`

Translating between Chinook stock IDs and human-readable names.

```{r, results = 'asis'}
knitr::kable(head(stock_chinook_fram, 5))
```

### `stock_coho_fram`

Translating between Coho stock IDs and human-readable names.

```{r, results = 'asis'}
knitr::kable(head(stock_coho_fram, 5))
```

### `fishery_chinook_fram`

Translating between Chinook fishery IDs and human-readable names.

```{r, results = 'asis'}
knitr::kable(head(fishery_chinook_fram, 5))
```

### `fishery_coho_fram`

Translating between Coho fishery IDs and human-readable names.


```{r, results = 'asis'}
knitr::kable(head(fishery_coho_fram, 5))
```

### `timestep_chinook_fram`

Translating between Chinook time-step IDs and human-readable names.

```{r, results = 'asis'}
knitr::kable(head(timestep_chinook_fram, 5))
```


### `timestep_coho_fram`

Translating between Coho time-step IDs and human-readable names.


```{r, results = 'asis'}
knitr::kable(head(timestep_coho_fram, 5))
```

