---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# framrosetta

<!-- badges: start -->
<!-- badges: end -->

`framrosetta` is a data library of look up tables for translating FRAM fisheries, stocks, and areas to other fishery data. `framrosetta` is part of the [FRAMverse R-Universe](https://framverse.r-universe.dev/packages).


## Installation

You can install `framrosetta` from R-Universe like so:

```r
install.packages("framrosetta", repos = "https://framverse.r-universe.dev")
```

Otherwise, if you have Rtools and either `{devtools}` or `{pak}` installed, you can
install `framrosetta` from source code like so:

```r
devtools::install_github("FRAMverse/framrosetta")    
```

or

```r
pak::pkg_install("FRAMverse/framrosetta")
```

```{r}
library(framrosetta)
```

## Key functions

`framrosetta` includes two functions to streamline mapping between fishery and stock IDs and names. `fishery_search` takes either a fishery ID number or a partial name and returns a tibble summarizing all fisheries that match; `stock_search` does the same for stocks. In both cases, the `species` argument must be provided to determine if the function should return the relevant `"CHINOOK"` or `"COHO"` fisheries / stocks. The `pattern` argument can take regular expressions, and is case insensitive. 


```{r}
fishery_search("kmz", "COHO")
fishery_search(50, "COHO")
stock_search("nooksack", "CHINOOK")
stock_search(21, "CHINOOK")
```


## Table summaries

`framrosetta` contains the following tables for translating FRAM fisheries, stocks, and areas to other fishery data or human readable formats:


### `rmis_fram`

Translating between FRAM and RMIS.

```{r, results = 'asis'}
knitr::kable(head(rmis_fram, 5))
```

### `tocas_fram`

Translating between FRAM and TOCAS.

```{r, results = 'asis'}
knitr::kable(head(tocas_fram, 5))
```

### `waft_fram`

Translating between WAFT and FRAM.

```{r, results = 'asis'}
knitr::kable(head(waft_fram, 5))
```


### `stock_chinook_fram`

Translating between Chinook stock IDs and human-readable names.

```{r, results = 'asis'}
knitr::kable(head(stock_chinook_fram, 5))
```

### `stock_coho_fram`

Translating between Coho stock IDs and human-readable names.

```{r, results = 'asis'}
knitr::kable(head(stock_coho_fram, 5))
```

### `fishery_chinook_fram`

Translating between Chinook fishery IDs and human-readable names.

```{r, results = 'asis'}
knitr::kable(head(fishery_chinook_fram, 5))
```

### `fishery_coho_fram`

Translating between Coho fishery IDs and human-readable names.


```{r, results = 'asis'}
knitr::kable(head(fishery_coho_fram, 5))
```

### `timestep_chinook_fram`

Translating between Chinook time-step IDs and human-readable names.

```{r, results = 'asis'}
knitr::kable(head(timestep_chinook_fram, 5))
```


### `timestep_coho_fram`

Translating between Coho time-step IDs and human-readable names.


```{r, results = 'asis'}
knitr::kable(head(timestep_coho_fram, 5))
```

